COG-ED Manuscript

### 2021-08-18 06_Paper/COG-ED/Manuscript.Rmd
Changed variable names and added NTLX score computation

  data_quest <- read.csv(here("Sampledata","COGERED_DATA.csv"), stringsAsFactors = FALSE, header = TRUE)

@@

      h2a_data <- rt[rt$level != 1,]
      h2a_data$level <- as.factor(h2a_data$level)

@@

      contrasts(h2a_data$level) <- cbind(c(1,-1,0), c(0,1,-1), c(1,0,-1))

@@

      hypothesis2a_anova <- summary(aov(h2a_data$meanrt ~ h2a_data$level))
      hypothesis2a_posthoc <- TukeyHSD(aov(h2a_data$meanrt ~ h2a_data$level))
      remove(h2a_data)

@@

  # aggregate NTLX data per participant per level

@@

@@

      h3a_data <- data_ntlx
      h3a_data$level <- as.factor(h3a_data$level)

@@

      contrasts(h3a_data$level) <- cbind(c(1,-1,0,0), c(0,1,-1,0), c(0,0,1,-1),
                                         c(1,0,-1,0), c(1,0,0,-1), c(0,1,0,-1))

@@

      hypothesis3a1_anova <- summary(aov(h3a_data$mental ~ h3a_data$level))
      hypothesis3a1_posthoc <- TukeyHSD(aov(h3a_data$mental ~ h3a_data$level))

      hypothesis3a2_anova <- summary(aov(h3a_data$physical ~ h3a_data$level))
      hypothesis3a2_posthoc <- TukeyHSD(aov(h3a_data$physical ~ h3a_data$level))

      hypothesis3a3_anova <- summary(aov(h3a_data$time ~ h3a_data$level))
      hypothesis3a3_posthoc <- TukeyHSD(aov(h3a_data$time ~ h3a_data$level))

      hypothesis3a4_anova <- summary(aov(h3a_data$performance ~ h3a_data$level))
      hypothesis3a4_posthoc <- TukeyHSD(aov(h3a_data$performance ~ h3a_data$level))

      hypothesis3a5_anova <- summary(aov(h3a_data$effort ~ h3a_data$level))
      hypothesis3a5_posthoc <- TukeyHSD(aov(h3a_data$effort ~ h3a_data$level))

      hypothesis3a6_anova <- summary(aov(h3a_data$frustration ~ h3a_data$level))
      hypothesis3a6_posthoc <- TukeyHSD(aov(h3a_data$frustration ~ h3a_data$level))

      remove(h3a_data)

>>>>

  data_quest <- read.csv(here("Sampledata","COGERED_DATA.csv"), stringsAsFactors = FALSE, header = TRUE)
  colnames(data_quest)[1] <- "set" # rename the first column

@@

      h1b_data <- rt[rt$level != 1,]
      h1b_data$level <- as.factor(h1b_data$level)

@@

      contrasts(h1b_data$level) <- cbind(c(1,-1,0), c(0,1,-1), c(1,0,-1))

@@

      hypothesis1b_anova <- summary(aov(h1b_data$meanrt ~ h1b_data$level))
      hypothesis1b_posthoc <- TukeyHSD(aov(h1b_data$meanrt ~ h1b_data$level))
      remove(h1b_data)

@@

  # compute index of rows in which the data sets change

  setindex <- c(1,which(data_quest$set != dplyr::lag(data_quest$set)),nrow(data_quest))

@@

  # feed NTLX data per participant per level into data frame

  for (i in 1:(length(setindex)-1)) {

    for (j in 1:4) {

      newdata <- data.frame(subject = data_quest$subject[setindex[i]], level = j,
                            mental = data_quest$nasa_tlx_01[setindex[i]+j+2],
                            physical = data_quest$nasa_tlx_02[setindex[i]+j+2],
                            time = data_quest$nasa_tlx_03[setindex[i]+j+2],
                            performance = data_quest$nasa_tlx_04[setindex[i]+j+2],
                            effort = data_quest$nasa_tlx_05[setindex[i]+j+2],
                            frustration = data_quest$nasa_tlx_06[setindex[i]+j+2])
      data_ntlx <- rbind(data_ntlx, newdata)
    }
  }

@@

      h1c_data <- data_ntlx
      h1c_data$level <- as.factor(h1c_data$level)

@@

      contrasts(h1c_data$level) <- cbind(c(1,-1,0,0), c(0,1,-1,0), c(0,0,1,-1),
                                         c(1,0,-1,0), c(1,0,0,-1), c(0,1,0,-1))

@@

      hypothesis1c1_anova <- summary(aov(h1c_data$mental ~ h1c_data$level))
      hypothesis1c1_posthoc <- TukeyHSD(aov(h1c_data$mental ~ h1c_data$level))

      hypothesis1c2_anova <- summary(aov(h1c_data$physical ~ h1c_data$level))
      hypothesis1c2_posthoc <- TukeyHSD(aov(h1c_data$physical ~ h1c_data$level))

      hypothesis1c3_anova <- summary(aov(h1c_data$time ~ h1c_data$level))
      hypothesis1c3_posthoc <- TukeyHSD(aov(h1c_data$time ~ h1c_data$level))

      hypothesis1c4_anova <- summary(aov(h1c_data$performance ~ h1c_data$level))
      hypothesis1c4_posthoc <- TukeyHSD(aov(h1c_data$performance ~ h1c_data$level))

      hypothesis1c5_anova <- summary(aov(h1c_data$effort ~ h1c_data$level))
      hypothesis1c5_posthoc <- TukeyHSD(aov(h1c_data$effort ~ h1c_data$level))

      hypothesis1c6_anova <- summary(aov(h1c_data$frustration ~ h1c_data$level))
      hypothesis1c6_posthoc <- TukeyHSD(aov(h1c_data$frustration ~ h1c_data$level))

      remove(h1c_data)
